%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{setspace}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins and spacing
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1.1in}
\addtolength{\textheight}{1.0in}
\setlength{\headheight}{14pt}
\setlength{\headsep}{0.5in}
\setlength{\footskip}{0.2in}
\setlength{\parskip}{0pt}
\setlength{\parsep}{4pt}
\setlength{\itemsep}{0pt}
\setlength{\topsep}{4pt}
\setlength{\partopsep}{4pt}
\linespread{0.95}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Adjust itemize spacing
\setlist[itemize]{leftmargin=*,noitemsep,topsep=2pt,partopsep=0pt}
\setlist[enumerate]{leftmargin=*,noitemsep,topsep=2pt,partopsep=0pt}

\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Frank Kocun} \\ \vspace{1pt}
    \small 437-240-6814 $|$ \href{mailto:frankkocun@gmail.com}{\underline{frankkocun@gmail.com}} $|$ 
    \href{https://linkedin.com/in/frank-kocun}{\underline{linkedin.com/in/frank-kocun}} $|$
    \href{https://github.com/Doomaloom}{\underline{github.com/Doomaloom}}
\end{center}

%---------OBJECTIVE------------
\vspace{-2pt}
\section{Candidate Summary}
  \begin{itemize}[leftmargin=0.15in, label={}]
  \item \small{Third-year Computer Science student with a strong foundation in full-stack development and a passion for application security. Eager to apply software engineering skills and knowledge from Information Security coursework to identifying, assessing, and mitigating vulnerabilities in a hands-on internship.}
  \end{itemize}

%-----------EDUCATION-----------
\vspace{-6pt}
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading 
      {University of Toronto Mississauga}{Sep. 2023 -- Jun. 2028}
      {Honours Bachelors of Science (H.Bsc), Computer Science, UTM Co-op Internship Program}{}
      \resumeSubItem{\textbf{Relevent Courses:} Intro to Information Security, Software Design, Algorithms Design and Analysis, Data Structures and Analysis, Operating Systems, Software Tools and Systems Programming }
  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\vspace{-6pt}
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, JavaScript, SQL, Go, Java, C, HTML, CSS\\
     \textbf{Developer Tools:} Docker, Google Cloud Run, Git, Firebase (Auth \& Security Rules), Linux, Agile/Scrum (SDLC)\\
     \textbf{Frameworks and Libraries:} Flask, Pandas, Matplotlib, Scikit-learn, JavaFx\\
     \textbf{Security Concepts:}  Web Application Vulnerabilities (OWASP Top 10), Attack Detection \& Log Analysis, Access Control
    }}
 \end{itemize}

 %-----------PROJECTS-----------
\vspace{-6pt}
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
          {\textbf{Deck Supervisor Admnistrative Web Tool} $|$ \emph{Firebase, Docker, Google Cloud, Flask, Pandas }}{May. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Built a scalable full-stack web application and backend API to automate class scheduling and roster generation.
            }
            \resumeItem{Implemented security controls including user authentication with Firebase Auth and database security rules to ensure users could only access their own data.}
            \resumeItem{Engineered backend services using Python (Flask) for data processing, deployed as a containerized service using Docker and Google Cloud Run.
            }
            \resumeItem{Designed and developed an intuitive, responsive web interface with JavaScript and Firebase.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{Machine Learning Prediction Model} $|$ \emph{Scikit-learn, Matplotlib, Git}}{Nov. 2024 -- present}
          \resumeItemListStart
            \resumeItem{Developed a machine learning model using Scikit-learn to analyze and predict patterns, demonstrating expertise in data preprocessing and predictive modeling.}
            \resumeItem{Employed Git version control to manage different modeling approaches.
            }
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Desktop Paint App} $|$ \emph{JavaFx, Scrum, OOP, Git}}{Oct. 2024 -- Nov. 2024}
          \resumeItemListStart
            \resumeItem{Engineered a desktop paint application with a team of 4, following the Scrum framework (SDLC).}
            \resumeItem{Led the implementation of software design patterns to enhance code modularity and readability.}
          \resumeItemListEnd
          
      
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\vspace{-6pt}
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Deck Supervisor}{Jan. 2025 -- Present}
      {City of Brampton}{Brampton, ON}
      \resumeItemListStart
        \resumeItem{Developed and managed lesson schematics for a team of 6 instructors, ensuring smooth operation.
        }
        \resumeItem{Acted as the primary point of contact for up to 75 concurrent customers, addressing inquiries and resolving complaints promptly (Strong communication skills for reporting).}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Lifeguard and Swim Instructor}{Mar. 2024 -- Present}
      {City of Brampton}{Brampton, ON}
      \resumeItemListStart
        \resumeItem{Monitored the safety of up to 75 guests, ensuring a secure environment.
        }
        \resumeItem{Strengthened customer relationships through clear communication and high-quality instruction.}
    \resumeItemListEnd
 
  \resumeSubHeadingListEnd




%-------------------------------------------
\end{document}
